Airspace configuration decision based on Monte-Carlo tree search

### 2018-01-31 article/article.tex
(+) debut etat de l'art

\usepackage{abstract}
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

@@

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting

@@

%----------------------------------------------------------------------------------------

@@

>>>>

\usepackage{abstract}
% Set the "Abstract" text to bold
\renewcommand{\abstractnamefont}{\normalfont\bfseries}
% Set the abstract itself to small italic text
\renewcommand{\abstracttextfont}{\normalfont\small\itshape}

% Allows customization of titles
\usepackage{titlesec}
% Roman numerals for the sections
\renewcommand\thesection{\Roman{section}}
% roman numerals for subsections
\renewcommand\thesubsection{\roman{subsection}}
% Change the look of the section titles
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{}
% Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{}

% Headers and footers
\usepackage{fancyhdr}
% All pages have headers and footers
\pagestyle{fancy}
% Blank out the default header
\fancyhead{}
% Blank out the default footer
\fancyfoot{}
% Custom header text
\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1}
% Custom footer text
\fancyfoot[RO,LE]{\thepage}
\usepackage{titling} % Customizing the title section

@@

%-----------------------------------------------------------------------------
%	TITLE SECTION
%-----------------------------------------------------------------------------

% Move the title up
\setlength{\droptitle}{-4\baselineskip}
% Article title formatting
\pretitle{\begin{center}\Huge\bfseries}
% Article title closing formatting
\posttitle{\end{center}}

@@

%-----------------------------------------------------------------------------

@@

The dynamic airspace configuration problem requires a model of the airspace. As
done in~\cite{sergeeva2017dynamic} or~\cite{treimuth2016branch} the airspace
is modelled via a graph. In those graphs, vertices represent elementary modules
and an edge links two adjacent modules. In~\cite{treimuth2016branch}, to be
able to produce a sequence of configurations, the graph is time dependent.
An other way to do the modelization, is to use a constrainted set of
configurations as in~\cite{gianazza2010forecasting} and~\cite{bloem2010dynamic}.
This way any configuration will match specified requirements, which can be
qualified hard constraints.

In most cases the cost of a configuration is based on the workload. Each
approach seems to give their own representation of the workload. For instance,
~\cite{bedouet2016} determined workload density proportionally to the time
spent by aircrafts in each sector. A simpler version~\cite{sergeeva2017dynamic}
only uses the number of aircratfs. On the other hand, more complex method,
involving many more inputs are also available, such as a neural network
forecasting the workload~\cite{gianazza2010forecasting}. This is the method we
are going to use in this paper.
